
---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(scales)
library(XML)
library(RJSONIO)
library(RCurl)
library(rvest)
library(stringr)
library(ggplot2)
library(plotly)
library(readxl)
library(rlist)
library(reshape2)
library(htmlwidgets)
library(sjmisc)
# We manually found the following link via the Web browser's Developer Tools in the Network tab.
# We found the json files

u = "https://static01.nyt.com/newsgraphics/2020/03/16/coronavirus-maps/a3c88fc852744c0bdb9ff9ee092cc5db785705d6/data/timeseries/en/USA.json"

tt = getURLContent(u, verbose = TRUE, followlocation = TRUE)

library(RJSONIO)
us = fromJSON(tt)


# The URL for the JSON changes each day. So today's URL, we want to find it in the current day's page.
# We get the top-level page

ny = htmlParse(getURLContent("https://www.nytimes.com/interactive/2020/us/coronavirus-us-cases.html?action=click&module=Top%20Stories&pgtype=Homepage"))

# Then we find the HTML elements that have an immediate child text node that contains the string USA.json.
js = xpathSApply(ny, "//*[contains(./text(), 'USA.json')]", xmlValue)

#These are <script> elements containing JavaScript, not JSON.
# But we can find the URL with a regular expression in these
u = gsub('.*"(https://[^"]+USA.json)".*', "\\1", js)
u = unique(u)
# There is only 1 URL repeated multiple times.

# So now we have these

tt = getURLContent(u, verbose = TRUE, followlocation = TRUE)
library(RJSONIO)
us = fromJSON(tt)



##get CA county data
County = list()
k = 1
for (i in 1:length(us$data)){
  all_data = us$data[[i]]
  if ((!is.na(all_data$hierarchy[3]))){
    if (all_data$hierarchy[3] == "USA-06" && all_data$display_name != "Unknown"){
      County[[k]] = all_data
      k = k + 1
    }
  }
}


## Get CA annd its county DATA
## Store them in a list 'County'
CA_data = us$data[[6]]
County[[k]] = CA_data

## Create lists for name; cases
Countyname = list()
cases = list()
deaths = list()
Dcases = list()
Ddeaths = list()
Alllist = list()
for (j in 1:length(County)){
  Countyname[j] = County[[j]]$display_name
  cases[[j]] = as.vector(County[[j]]$cases)
  deaths[[j]] = as.vector(County[[j]]$deaths)
  Dcases[[j]] = as.vector(County[[j]]$cases) - c(0, as.vector(County[[j]]$cases))[1:length(as.vector(County[[j]]$cases))]
  
  Ddeaths[[j]] = as.vector(County[[j]]$deaths) - c(0, as.vector(County[[j]]$deaths))[1:length(as.vector(County[[j]]$deaths))]
}
#store the cumulative cases as dataframe
df = as.data.frame(list.cbind(cases))
colnames(df) = as.vector(Countyname)

#store the cumulative deaths as dataframe
df1 = as.data.frame(list.cbind(deaths))
colnames(df1) = as.vector(Countyname)

#store the daily cases as dataframe
df2 = as.data.frame(list.cbind(Dcases))
colnames(df2) = as.vector(Countyname)

#store the daily deaths as dataframe
df3 = as.data.frame(list.cbind(Ddeaths))
colnames(df3) = as.vector(Countyname)

## get population for counties
Pop = read_excel("~/Desktop/UCD/Third Year/sta141b/hw5/Book2.xlsx")
Pop$California = CA_data$population
Pop = do.call("rbind", replicate(nrow(df2), Pop, simplify = FALSE))
Pop = as.data.frame(Pop)



##get the range of date
timerange = seq(as.Date(CA_data$range[1]), as.Date(CA_data$range[2]), by = "day")
df$time = timerange
df1$time = timerange
df2$time = timerange
df3$time = timerange

## reshape the data into a form that can be used by ggplot
finaldata = melt(df2, id.vars='time')

## plot
k = highlight_key(finaldata, ~variable)
pl = ggplot(data = k, aes(time, value, col = variable)) + geom_line()
plty = ggplotly(pl, tooltip = c("variable", "time", "value"))
graph = highlight(plty, on = "plotly_click", off = "plotly_doubleclick")

saveWidget(graph, "try.html", selfcontained = FALSE)


## cat(toJSON(df, container = T))

## create pro_rated values: df4
pro = list()
for( i in (1:length(County))){
  pro[[i]] = round(df2[,i]/Pop[,i]*10000,2)  ##pro_rate
}
df4 = as.data.frame(list.cbind(pro))
colnames(df4) = as.vector(Countyname)

##get the data to add in the tooltip: daily cases; daily deaths; cumulatives; and dates
tooldata = list()
for (c in 1 : length(County)){
tooldata[[c]] = as.vector(paste(df$time, df[,c],df1[,c],df2[,c],df3[,c],df4[,c],sep= ";'           '"))
}
t = as.data.frame(tooldata)
colnames(t) = as.vector(Countyname)


# ##get the color with respect to daily cases

Dcolor = list()
for (m in 1:58){
  data = rescale(df4[,m], to = c(0,1))
  data = abs(as.numeric(data))
  Dcolor[[m]] = rgb(1-data,data,1)
}
Dcolor = as.data.frame(list.cbind(Dcolor))
cat("var CACols =", toJSON(Dcolor), ";", file = "2.js")
